HCI Final Paper

### 2015-12-06 sigchi-latex-proceedings 2/final-paper.tex
Create Final-Paper.tex

% Make sure hyperref comes last of your loaded packages, to give it a
% fighting chance of not being over-written, since its job is to
% redefine many LaTeX commands.
\definecolor{linkColor}{RGB}{6,125,233}
\hypersetup{%
  pdftitle={HCI Draft Paper},
  pdfauthor={LaTeX},
  pdfkeywords={SIGCHI, proceedings, archival format},
  bookmarksnumbered,
  pdfstartview={FitH},
  colorlinks,
  citecolor=black,
  filecolor=black,
  linkcolor=black,
  urlcolor=linkColor,
  breaklinks=true,
}

@@

\title{HCI Draft Paper}

@@

@@

\section{Preliminary Results}
The mean task completion time for each participant on each interface is outlined in the following table.

@@

\section{Preliminary Discussion}
While the differences between speed and accuracy are statistically insignificant, a discussion can still take place. The stacked interface was perceived by the participants to be faster, which held when examining the data. This is inline with previous literature like the work of Warr and Chi [7]. However, this begs the question: why is stacked interface perceived as quicker? It’s possible this is due to the fact that the motion of the cards is toward the user rather than down. In addition, with the stacked interface the user can control the sensitivity of the scroll by scrolling from higher up on the screen. This allows users to more quickly traverse a long list of apps at the cost of some granularity of motion.

@@

@@

\section{Appendix}
\section{Appendix A: Participant Tasks}
\textbf{Task Block 1}
\begin{itemize}
\item Task 1: Start at Home Screen. Open Contacts. Find “Ishan Thukral”. Copy his phone number to the clipboard. Switch to Messages.
\item Task 2: In Messages, create a new message. Paste the phone number that you copied. Switch to Photos.
\item Task 3: In Photos, find a photo of a computer. Share this photo to Messages and with Ishan.
\item Task 4: Switch back to Contacts then go to the Home Screen. Stop. Give phone to experimenter.
\end{itemize}

\textbf{Task Block 2}
\begin{itemize}
\item Task 1: Start at Home Screen. Open Email and open the most recent message. Copy the restaurant name from the message body to the clipboard. Switch to Yelp.
\item Task 2: In Yelp, find the restaurant using the name. Copy the address of the restaurant to clipboard. Switch to Google Maps.
\item Task 3: In Google Maps, paste the address as destination. Find out how long it takes you to get there using transit. Switch to Email.
\item Task 4: In Email, reply to the message with the transit time. Go to Home Screen. Stop. Give phone to experimenter.
\end{itemize}

\textbf{Task Block 3}
\begin{itemize}
\item Task 1: Start at Home Screen. Open Internet. Go to m.reddit.com. Tap “Login/Register”. Switch to Notes.
\item Task 2: In Notes, open up note titled “Reddit Login Information”.  Copy the email address. Switch to Internet.
\item Task 3: In Internet, paste the email address in the login screen. Switch to Notes.
\item Task 4: In Notes, copy the password. Switch to Internet.
\item Task 5: In Internet, paste the password. Login to the site. Go to Home Screen. Stop. Give phone to experimenter.
\end{itemize}

\section{Appendix B: Experimental Setup}
\textbf{Task Block 1}
Experimenter opens apps in this order: Messages, Photos.
Task complication: apps won’t be right next to each other when participant opens switcher.

\textbf{Task Block 2}
Experimenter opens apps in this order: Contacts, Yelp, Photos, Google Maps, Messages
Task complication: participants have to find the apps they are switching to in a non-ordered list of open apps.

\textbf{Task Block 3}
Experimenter opens apps in this order: Internet, Google Maps, Yelp, Email, Photos, Messages, Contacts.
Task complication: Participant will have to scroll to the end of the app list to switch to Internet.

\section{Appendix C: Consent Form}
I hereby consent to participate in the research study conducted by Ajit Pawar, Colin White, Ishan Thukral, Kyra Assaad, and Zach Munro-Cape as part of the Fall 2015 semester project for CSC428, Human-Computer Interaction, offered by the Department of Computer Science at the University of Toronto.

I agree to participate in this study whose purpose is to evaluate the accuracy and speed of stacked/unstacked smartphone multitasking interfaces.

I understand that:
\begin{itemize}
\item The study uses direct observation.
\item There are no significant risks incurred by participating in this experiment.
\item I will receive no compensation of my participation.
\item I am free to withdraw at any time during the study without the need to give any explanation or reason and without any penalty.
\item All material and results will be kept confidential, and, in particular, that my name and any identifying or identified information will not be associated with the data.
\item I can contact the course lecturer, Oliver St. Cyr (stcyr@mie.utoronto.ca), with any questions or concerns.
\end{itemize}

\textbf{PARTICIPANT:}\\
Name (please print): \\
Signature:\\
Date:\\

\textbf{INVESTIGATOR:}\\
Name:\\
Signature:\\

\section{Appendix D: Entry Survey}
What is your age? (choose one)\\
* Under 17\\
* 17-23\\
* 24-30\\
* 31-40\\
* 40+

What is your gender? (choose one)\\
* Male\\
* Female\\
* Trans*\\
* Other

Are you: (choose one)\\
* Right-handed\\
* Left-handed\\
* Ambidextrous

Have you used the Android operating system before? (choose one)\\
* Yes\\
* No

Do you own an Android phone? (choose one)\\
* Yes\\
* No

What version of Android are you most comfortable with? (choose one)\\
* KitKat\\
* Lollipop\\
* Marshmallow\\
* I’m not sure\\
* Other

What model of phone do you have? (write below)\\

\section{Appendix E: Exit Survey}
With what speed did you perceive you were able to switch between applications?\\
KitKat (Non-stacked)\\
* Sluggish\\
* Slow\\
* Average\\
* Fast\\
* Lightning Fast

Lollipop(Stacked)\\
* Sluggish\\
* Slow\\
* Average\\
* Fast\\
* Lightning Fast\\

With what accuracy did you perceive you were able to switch between applications?\\
KitKat (Non-stacked)\\
* Terrible accuracy\\
* Not very accurate\\
* Average\\
* Fairly accurate\\
* Got it every time

Lollipop(Stacked)\\
* Terrible accuracy\\
* Not very accurate\\
* Average\\
* Fairly accurate\\
* Got it every time\\

Do you have a preference on using either OS for its multitasking interface?\\
* KitKat (Non-stacked)\\
* Lollipop (Stacked)\\
* No preference\\

>>>>

% Make sure hyperref comes last of your loaded packages, to give it a
% fighting chance of not being over-written, since its job is to
% redefine many LaTeX commands.
\definecolor{linkColor}{RGB}{6,125,233}
\hypersetup{%
  pdftitle={HCI Final Paper},
  pdfauthor={Kyra Assaad, Zach Munro-Cape, Ajit Pawar, Ishan Thukral, \& Colin White},
  pdfkeywords={HCI, multitasking, application switching},
  bookmarksnumbered,
  pdfstartview={FitH},
  colorlinks,
  citecolor=black,
  filecolor=black,
  linkcolor=black,
  urlcolor=linkColor,
  breaklinks=true,
}

@@

\title{HCI Final Paper}

@@

\section{Abstract}

@@

\section{Results}
The mean task completion time for each participant on each interface is outlined in the following table.

@@

\section{Discussion}
While the differences between speed and accuracy are statistically insignificant, a discussion can still take place. The stacked interface was perceived by the participants to be faster, which held when examining the data. This is inline with previous literature like the work of Warr and Chi [7]. However, this begs the question: why is stacked interface perceived as quicker? It’s possible this is due to the fact that the motion of the cards is toward the user rather than down. In addition, with the stacked interface the user can control the sensitivity of the scroll by scrolling from higher up on the screen. This allows users to more quickly traverse a long list of apps at the cost of some granularity of motion.

@@

\section{Conclusion}

@@
